---
title: "ABCrf_3pops"
author: "karine Durand"
date: "7 mai 2019"
output: html_document
---
---
title: "Bpfile_2pops_pacaCVCST53"
author: "karine Durand"
date: "18 mars 2019"

output:
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}
#Installing and loading the R package abcrf
#install.packages("abcrf") # To install the abcrf package (version 1.6)
library(abcrf) # To load the package.
library(readr)
library("plyr", lib.loc="~/R/x86_64-pc-linux-gnu-library/3.4")
f <- function(x){
  m <- mean(x, na.rm = TRUE)
  x[is.na(x)] <- m
  x
}
```

## Reading data: option 2 - using a.txtfile

corresponding to the scenario indices,p columns of parameters and k columns of summary statistics, the
first row is the column labels. The field separator character being a white space.


```{r cars}
###ormule#############
paramSI1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POP_SI_homo/priorfile", col_names = T)
paramSI3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POP_SI_hetero/priorfile", col_names = T)

paramAM1<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POP_AM_homo/priorfile", col_names = T)
paramAM3<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POP_AM_hetero/priorfile", col_names = T)
paramGhostCA1<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POP_ghost_homoCASA/priorfile", col_names = T)
paramGhostCA3<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POP_ghost_heteroCASA/priorfile", col_names = T)
paramGhostSA1<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POP_ghost_homoSACA//priorfile", col_names = T)
paramGhostSA3<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POP_ghost_heteroSACA//priorfile", col_names = T)

paramAdmixCA1<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POPS_admixCA/priorfile", col_names = T)
paramAdmixCA3<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POPS_admixCAhetero//priorfile", col_names = T)
paramAdmixSA1<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POPS_admixSA//priorfile", col_names = T)
paramAdmixSA3<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POPS_admixSAhetero//priorfile", col_names = T)


rbind.fill(paramSI1,paramSI3,paramAM1,paramAM3,paramGhostCA1,paramGhostCA3,paramGhostSA1,paramGhostSA3,paramAdmixCA1,paramAdmixCA3,paramAdmixSA1,paramAdmixSA3)->param


rbind.fill(paramSI3,paramAM3,paramGhostCA3,paramGhostSA3,paramAdmixCA3,paramAdmixSA3)->param
#import des stats

SI1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POP_SI_homo/ABCstat.txt", col_names = T)
SI3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POP_SI_hetero/ABCstat.txt", col_names = T)

AM1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POP_AM_homo/ABCstat.txt",  col_names = T)
AM3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POP_AM_hetero//ABCstat.txt",  col_names = T)
GhostCA1<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POP_ghost_homoCASA/ABCstat.txt",  col_names = T)
GhostCA3<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POP_ghost_heteroCASA/ABCstat.txt",  col_names = T)
GhostSA1<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POP_ghost_homoSACA//ABCstat.txt",  col_names = T)
GhostSA3<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POP_ghost_heteroSACA/ABCstat.txt",  col_names = T)
ADMIXCA1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POPS_admixCA/ABCstat.txt",  col_names = T)
ADMIXCA3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POPS_admixCAhetero//ABCstat.txt",  col_names = T)
ADMIXSA1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POPS_admixSA/ABCstat.txt",  col_names = T)
ADMIXSA3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen3pops/3POPS_admixSAhetero//ABCstat.txt",  col_names = T)

#MISSING DATA
obs798 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/obs/798_orthologues_multi19pauca/summaryobs_3pops",  col_names = T)



obs798<-obs798[,-c(1,64:65,100,101,136:137)]

nlinesFul=10000
SI1=SI1[c(1:nlinesFul),-c(1,64:65,100,101,136:137)]
SI3=SI3[c(1:nlinesFul),-c(1,64:65,100,101,136:137)]
AM1=AM1[c(1:nlinesFul),-c(1,64:65,100,101,136:137)]
AM3=AM3[c(1:nlinesFul),-c(1,64:65,100,101,136:137)]
GhostCA1=GhostCA1[c(1:nlinesFul),-c(1,64:65,100,101,136:137)]
GhostCA3=GhostCA3[c(1:nlinesFul),-c(1,64:65,100,101,136:137)]
GhostSA1=GhostSA1[c(1:nlinesFul),-c(1,64:65,100,101,136:137)]
GhostSA3=GhostSA3[c(1:nlinesFul),-c(1,64:65,100,101,136:137)]
ADMIXCA1=ADMIXCA1[c(1:nlinesFul),-c(1,64:65,100,101,136:137)]
ADMIXCA3=ADMIXCA3[c(1:nlinesFul),-c(1,64:65,100,101,136:137)]
ADMIXSA1=ADMIXSA1[c(1:nlinesFul),-c(1,64:65,100,101,136:137)]
ADMIXSA3=ADMIXSA3[c(1:nlinesFul),-c(1,64:65,100,101,136:137)]

SI1 <- apply(SI1 , 2, f)
SI3 <- apply(SI3 , 2, f)
AM1  <- apply(AM1  , 2, f)
AM3  <- apply(AM3 , 2, f)
GhostCA1 <- apply(GhostCA1  , 2, f)
GhostCA3 <- apply(GhostCA3  , 2, f)
GhostSA1 <- apply(GhostSA1  , 2, f)
GhostSA3 <- apply(GhostSA3  , 2, f)
ADMIXCA1 <- apply(ADMIXCA1  , 2, f)
ADMIXCA3 <- apply(ADMIXCA3  , 2, f)
ADMIXSA1 <- apply(ADMIXSA1   , 2, f)
ADMIXSA3 <- apply(ADMIXSA3   , 2, f)


rbind.na(SI1,SI3,AM1,AM3,GhostCA1,GhostCA3,GhostSA1,GhostSA3,ADMIXCA1,ADMIXCA3,ADMIXSA1,ADMIXSA3)->sumstat
rbind.na(SI3,AM3,GhostCA3,GhostSA3,ADMIXCA3,ADMIXSA3)->sumstat



modindex <- as.factor(c(rep("SI1",10000),rep("SI3",10000),rep("AM1",10000) , rep("AM3",10000),rep("GhostCA1",10000),rep("GhostCA3",10000) ,rep("GhostSA1",10000),rep("GhostSA3",10000),rep("ADMIXCA1",10000),rep("ADMIXCA3",10000),rep("ADMIXSA1",10000),rep("ADMIXSA3",10000)))


modindex <- as.factor(c(rep("SI3",10000), rep("AM3",10000),rep("GhostCA3",10000) ,rep("GhostSA3",10000),rep("ADMIXCA3",10000),rep("ADMIXSA3",10000)))


#dfparam = as.data.frame(param)

dfparam=as.data.frame(param)
View(dfparam)
index1 <-as.factor(modindex) # To store the model 1 indexes.

#dfsumsta = as.data.frame(sumsta)
dfsumsta = as.data.frame(sumstat)
View(dfsumsta)
#n try = k/3 k nombre de summary stats =variable 42 ntry=14
rf3POPS<- list(modindex=modindex,param=dfparam, sumsta=dfsumsta)
data3POPS <- data.frame(modindex, sumstat)
model.rf3POPSI<- abcrf(modindex~., data=data3POPS ,ntree=1000,paral = TRUE)
err.rf <- err.abcrf(model.rf3POPSI,data3POPS)

```

## PLOTS 

Confusion matrix:

```{r pressure}
model.rf3POPSI


#aec les data obs
plot(model.rf3POPSI, data3POPS, obs=obs798[1,])
predict(model.rf3POPSI, obs798, data3POPS, ntree=1000)


```
#####################  Inference des parametres 
# inference d'un parametre
Given a reg-ABC-RF object and a new value of the summary statistics, densityPlot gives the
corresponding posterior density plot of the parameter, as well as the prior (in grey)

```{r}
N1 <- rf3POPS$param$N1[modindex == "SI3"]
dataN1 <- data.frame(N1, sumstat)
dataN1 <-dataN1[20001:30000,]
model.rf.N1 <- regAbcrf(N1~., dataN1, ntree=1000)
plot(model.rf.N1)
pdf(file="posterieurprobaTS_AM1")
densityPlot(model.rf.N1, obs798, dataN1, ylab="density", main = "Posterior density of N1")
dev.off()
N2 <- rf3POPS$param$N2[modindex == "SI3"]
dataN2 <- data.frame(N2, sumstat)
dataN2 <-dataN2[20001:30000,]
model.rf.N2 <- regAbcrf(N2~., dataN2, ntree=1000)
plot(model.rf.N2)
pdf(file="posterieurprobaN2_AM1")
densityPlot(model.rf.N2, obs798, dataN2, ylab="density", main = "Posterior density of N2")
N3 <- rf3POPS$param$N3[modindex == "SI3"]
dataN3 <- data.frame(N3, sumstat)
dataN3 <-dataN3[20001:30000,]
model.rf.N3 <- regAbcrf(N3~., dataN3, ntree=1000)
densityPlot(model.rf.N2, obs798, dataN2, ylab="density", main = "Posterior density of N3")
Na1 <- rf3POPS$param$Na1[modindex == "SI3"]
dataNa1 <- data.frame(Na1, sumstat)
dataNa1 <-dataNa1[20001:30000,]
model.rf.Na1 <- regAbcrf(Na1~., dataNa1, ntree=1000)
densityPlot(model.rf.Na1, obs798, dataNa1, ylab="density", main = "Posterior density of Na1")
Na2 <- rf3POPS$param$Na2[modindex == "SI3"]
dataNa2 <- data.frame(Na2, sumstat)
dataNa2 <-dataNa2[20001:30000,]
model.rf.Na2 <- regAbcrf(Na2~., dataNa2, ntree=1000)
densityPlot(model.rf.Na2, obs798, dataNa2, ylab="density", main = "Posterior density of Na2")
Na <- rf3POPS$param$Na[modindex == "SI3"]
dataNa <- data.frame(Na, sumstat)
dataNa <-dataNa[20001:30000,]
model.rf.Na <- regAbcrf(Na~., dataNa, ntree=1000)
densityPlot(model.rf.Na, obs798, dataNa, ylab="density", main = "Posterior density of Na")
####
TS1 <-  rf3POPS$param$Tsplit1[modindex == "SI3"]
dataTS1 <- data.frame(TS1, sumstat)
dataTS1  <-dataTS1[20001:30000,]
model.rf.TS1 <- regAbcrf(TS1~., dataTS1, ntree=1000)
model.rf.TS1
densityPlot(model.rf.TS1, obs798, dataTS1, ylab="density", main = "Posterior density of TS1")
TS2 <-  rf3POPS$param$Tsplit2[modindex == "SI3"]
dataTS2 <- data.frame(TS2, sumstat)
dataTS2  <-dataTS2[20001:30000,]
model.rf.TS2 <- regAbcrf(TS2~., dataTS2, ntree=1000)
model.rf.TS2
densityPlot(model.rf.TS2, obs798, dataTS2, ylab="density", main = "Posterior density of TS2")
####TAM
TAM1 <-  rf3POPS$param$Tam1[modindex == "SI3"]
dataTAM1 <- data.frame(TAM1, sumstat)
dataTAM1  <-dataTAM1[20001:30000,]
model.rf.TAM1 <- regAbcrf(TAM1~., dataTAM1, ntree=1000)
densityPlot(model.rf.TAM1, obs798, dataTAM1, ylab="density", main = "Posterior density of TAM1")

TAM3 <-  rf3POPS$param$Tam3[modindex == "SI3"]
dataTAM3 <- data.frame(TAM3, sumstat)
dataTAM3  <-dataTAM3[20001:30000,]
model.rf.TAM3 <- regAbcrf(TAM3~., dataTAM3, ntree=1000)
densityPlot(model.rf.TAM3, obs798, dataTAM3, ylab="density", main = "Posterior density of TAM3")

P<-   rf3POPS$param$P[modindex == "ADMIXCA3"]
dataP<- data.frame(P, sumstat)
dataP   <-dataP[80001:90000,]
model.rf.P<- regAbcrf(P~., dataP, ntree=1000)
densityPlot(model.rf.P, obs798, dataP, ylab="density", main = "Posterior density of P")
##
M23<-   rf3POPS$param$M23[modindex == "SI3"]
dataM23 <- data.frame(M23, sumstat)
dataM23   <-dataM23[20001:30000,]
model.rf.M23<- regAbcrf(M23~., dataM23, ntree=1000)
model.rf.TM23
densityPlot(model.rf.M23, obs798, dataM23, ylab="density", main = "Posterior density of M23")
M32<-   rf3POPS$param$M32[modindex == "SI3"]
dataM32 <- data.frame(M32, sumstat)
dataM32   <-dataM32[20001:30000,]
model.rf.M32<- regAbcrf(M32~., dataM32, ntree=1000)
model.rf.TM32
densityPlot(model.rf.M32, obs798, dataM32, ylab="density", main = "Posterior density of M32")

M13<-   rf3POPS$param$M13[modindex == "SI3"]
dataM13 <- data.frame(M13, sumstat)
dataM13   <-dataM13[20001:30000,]
model.rf.M13<- regAbcrf(M13~., dataM13, ntree=1000)
densityPlot(model.rf.M13, obs798, dataM13, ylab="density", main = "Posterior density of M13")

M31<-   rf3POPS$param$M31[modindex == "SI3"]
dataM31 <- data.frame(M31, sumstat)
dataM31   <-dataM31[20001:30000,]
model.rf.M31<- regAbcrf(M31~., dataM31, ntree=1000)
densityPlot(model.rf.M31, obs798, dataM31, ylab="density", main = "Posterior density of M31")

M1<-  rf3POPS$param$M1[modindex == "ADMIXCA3"]
dataM1 <- data.frame(M1, sumstat)
dataM1   <-dataM1[80001:90000,]
model.rf.M1<- regAbcrf(M1~., dataM1, ntree=1000)
densityPlot(model.rf.M1, obs798, dataM1, ylab="density", main = "Posterior density of M1")
M2<-  rf3POPS$param$M2[modindex == "ADMIXCA3"]
dataM2 <- data.frame(M2, sumstat)
dataM2   <-dataM2[80001:90000,]
model.rf.M1<- regAbcrf(M1~., dataM1, ntree=1000)
densityPlot(model.rf.M2, obs798, dataM2, ylab="density", main = "Posterior density of M2")
####REGRESSION
####classification par regression paramtre explorer TS
#The used formula means that we are interested in explaining the parameter
# TS thanks to all the remaining columns of dataTS
TS <-  rouxN10000$param$Tsplit[modindex == "AM1"]
dataTS <- data.frame(TS, sumstatN10000)
dataTS  <-dataTS[70001:80000,]
model.rf.TS <- regAbcrf(TS~., dataTS, ntree=500,min.node.size = 5, paral = TRUE, mtry =14)
model.rf.TS

#Graphical representations to access the performance of the method
errorOOB <- err.regAbcrf(object = model.rf.TS , training = dataTS,paral = TRUE)
plot(errorOOB)

# The contributions of the 25 most important summary statistics are
# represented
plot(x = model.rf.TS, n.var = 25)

###prediction
pred.obsTS1 <- predict(object = model.rf.TS1, obs = obs798,training = dataTS1, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsTS2 <- predict(object = model.rf.TS2, obs = obs798,training = dataTS2, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsTam1 <- predict(object = model.rf.TAM1, obs = obs798,training = dataTAM1, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsTam3 <- predict(object = model.rf.TAM3, obs = obs798,training = dataTAM3, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsM23 <- predict(object = model.rf.M23, obs = obs798,training = dataM23, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsM32 <- predict(object = model.rf.M32, obs = obs798,training = dataM32, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsM13 <- predict(object = model.rf.M13, obs = obs798,training = dataM23, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsM31 <- predict(object = model.rf.M31, obs = obs798,training = dataM32, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsM1 <- predict(object = model.rf.M1, obs = obs798,training = dataM1, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsM2 <- predict(object = model.rf.M2, obs = obs798,training = dataM2, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsN1 <- predict(object = model.rf.N1, obs = obs798,training = dataN1, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsN2 <- predict(object = model.rf.N2, obs = obs798,training = dataN2, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsN3 <- predict(object = model.rf.N3, obs = obs798,training = dataN3, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsNa <- predict(object = model.rf.Na, obs = obs798,training = dataNa, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsNa1 <- predict(object = model.rf.Na1, obs = obs798,training = dataNa1, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsNa2<- predict(object = model.rf.Na2, obs = obs798,training = dataNa2, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsP<- predict(object = model.rf.P, obs = obs798,training = dataP, quantiles = c(0.025,0.975),paral = TRUE)
# The 2.5 and 97.5 order quantiles are computed by specifying
# quantiles = c(0.025,0.975).
#Posterior mean can be retrieved by
pred.obsP$expectation
pred.obsP$quantiles
pred.obsP$variance
pred.obsTS1$expectation
pred.obsTS1$quantiles
pred.obsTS1$variance
pred.obsTS2$expectation
pred.obsTS2$quantiles
pred.obsTS2$variance
pred.obsTam1$expectation
pred.obsTam1$quantiles
pred.obsTam1$variance
pred.obsTam3$expectation
pred.obsTam3$quantiles
pred.obsTam3$variance
pred.obsM23$expectation
pred.obsM23$quantiles
pred.obsM23$variance
pred.obsM32$expectation
pred.obsM32$quantiles
pred.obsM32$variance
pred.obsM13$expectation
pred.obsM13$quantiles
pred.obsM13$variance
pred.obsM31$expectation
pred.obsM31$quantiles
pred.obsM31$variance
pred.obsN1$expectation
pred.obsN1$quantiles
pred.obsN1$variance
pred.obsN2$expectation
pred.obsN2$quantiles
pred.obsN2$variance
pred.obsN3$expectation
pred.obsN3$quantiles
pred.obsN3$variance
pred.obsNa$expectation
pred.obsNa$quantiles
pred.obsNa$variance
pred.obsNa1$expectation
pred.obsNa1$quantiles
pred.obsNa1$variance
pred.obsNa2$expectation
pred.obsNa2$quantiles
pred.obsNa2$variance
pred.obsM1$expectation
pred.obsM1$quantiles
pred.obsM1$variance

```
