---
title: "script_abc_choix_model.rmd"
author: "karine Durand"
date: "8 mars 2019"
output: html_document
---

```{r setup, include=FALSE}
#Installing and loading the R package abcrf
#install.packages("abcrf") # To install the abcrf package (version 1.6)
library(abcrf) # To load the package.
library(readr)
library("plyr", lib.loc="~/R/x86_64-pc-linux-gnu-library/3.4")
f <- function(x){
  m <- mean(x, na.rm = TRUE)
  x[is.na(x)] <- m
  x
}
```

## Reading data: option 2 - using a.txtfile

corresponding to the scenario indices,p columns of parameters and k columns of summary statistics, the
first row is the column labels. The field separator character being a white space.


```{r cars}
###ormule#############
paramSI1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/fastSimBac_linux/fastsimbac_alignement_13paucacvcmulti/SI1/priorfile", col_names = T)

paramIM1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/fastSimBac_linux/fastsimbac_alignement_13paucacvcmulti/IM1//priorfile", col_names = T)

paramSC1<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/fastSimBac_linux/fastsimbac_alignement_13paucacvcmulti/SC1/priorfile", col_names = T)

paramAM1<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/fastSimBac_linux/fastsimbac_alignement_13paucacvcmulti/AM1/priorfile", col_names = T)


rbind.fill(paramSI1,paramIM1,paramSC1,paramAM1)->paramN10000

#import des stats

SI1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/fastSimBac_linux/fastsimbac_alignement_13paucacvcmulti/SI1/ABCstat", col_names = T)

SC1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/fastSimBac_linux/fastsimbac_alignement_13paucacvcmulti/SC1/ABCstat",  col_names = T)


IM1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/fastSimBac_linux/fastsimbac_alignement_13paucacvcmulti/IM1/ABCstat",  col_names = T)


AM1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/fastSimBac_linux/fastsimbac_alignement_13paucacvcmulti/AM1/ABCstat",  col_names = T)
#AM2 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/AM_Nhomo_Mhetero/ABCstat.txt",  
#MISSING DATA
SI1<-SI1[1:1000,-c(1,3,5,7,9,11,13,15,17,19,21,23,25,27,29,31,32,33,35,37,39,41,43,45,46,47,49,51,53,55,57,59,61,63,65,67,69,71,73)]
SC1<-SC1[1:1000,-c(1,3,5,7,9,11,13,15,17,19,21,23,25,27,29,31,32,33,35,37,39,41,43,45,46,47,49,51,53,55,57,59,61,63,65,67,69,71,73)]
IM1<-IM1[1:1000,-c(1,3,5,7,9,11,13,15,17,19,21,23,25,27,29,31,32,33,35,37,39,41,43,45,46,47,49,51,53,55,57,59,61,63,65,67,69,71,73)]
AM1<-AM1[1:1000,-c(1,3,5,7,9,11,13,15,17,19,21,23,25,27,29,31,32,33,35,37,39,41,43,45,46,47,49,51,53,55,57,59,61,63,65,67,69,71,73)]

paramSI1<-paramSI1[1:1459,]
paramAM1<-paramAM1[1:1459,]
paramIM1<-paramIM1[1:1459,]
paramSC1<-paramSC1[1:1459,]


SI1 <- apply(SI1 , 2, f)
#SINhetero  <- apply(SINhetero  , 2, f)
SC1  <- apply(SC1  , 2, f)
#SC2  <- apply(SC2  , 2, f)
#SC3  <- apply(SC3  , 2, f)
#SC4  <- apply(SC4  , 2, f)
IM1  <- apply(IM1  , 2, f)
#IM2  <- apply(IM2  , 2, f)
#IM3  <- apply(IM3  , 2, f)
#IM4  <- apply(IM4  , 2, f)
AM1  <- apply(AM1  , 2, f)
#AM2  <- apply(AM2  , 2, f)
#AM3  <- apply(AM3  , 2, f)
#AM4  <- apply(AM4  , 2, f)

rbind.na(SI1,IM1,SC1,AM1)->sumstatN10000

obsaln <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/obs/obs_alignement13pauca/obsalnmsums",  col_names = T)
obsaln<-obsaln[1 ,-c(1,3,5,7,9,11,13,15,17,19,21,23,25,27,29,31,32,33,35,37,39,41,43,45,46,47,49,51,53,55,57,59,61,63,65,67,69,71,73)]


#param<- read_delim("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/paramtot",";", escape_double = FALSE,  trim_ws = #TRUE)
#sumsta <- read_delim("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/sumsta",  ";", escape_double = FALSE, trim_ws = TRUE)

modindex <- as.factor(c(rep("SI1",1000), c(rep("IM1",1000),rep("SC1",1000),rep("AM1",1000)))
x <- as.factor(c(rep("SI1",1330), rep("SC1",1330),rep("AM1",1330),
                 rep("obsaln",1))) 

#dfparam = as.data.frame(param)

dfparam=as.data.frame(paramN10000)
View(dfparam)


#dfsumsta = as.data.frame(sumsta)
dfsumsta = as.data.frame(sumstatN10000)
View(dfsumsta)
#n try = k/3 k nombre de summary stats =variable 42 ntry=14
rouxN10000 <- list(modindex=modindex,param=dfparam, sumsta=dfsumsta)
dataN10000 <- data.frame(modindex, sumstatN10000)
model.rf1ROUX<- abcrf(modindex~., data=dataN10000 ,ntree=500,paral = TRUE)
model.rf1ROUX
#acp classic
datafast=(as.data.frame(rbind(sumstatN10000,obsaln)))
library(ade4)
acp1 <- dudi.pca(datafast,scannf=F,nf=2)
s.class(acp1$li,x) # avec des ellipses de confiance

#Predict and evaluate the posterior probability of the MAP for new data using an ABC-RF object
modindexA <- XROUX $modindex[1:140000]
sumstaA <- XROUX $sumsta[1:140000,]
dataA <- data.frame(modindexA, sumstaA)
model.rfA <- abcrf(modindexA~., dataA, ntree=100)
predict(model.rf1ROUX, obsaln, data1, ntree=500)
err.rf <- err.abcrf(model.rf1ROUX,dataN10000)
#data.poi <- list(modindex=index1,param=dfparam, sumsta=dfsumsta)
```

## PLOTS 

Confusion matrix:

```{r pressure}
model.rf1ROUX


#aec les data obs
plot(model.rf1ROUX, dataN10000, obs=obsaln[1,])

# Prediction is complete by
#pred.obsPoi <- predict(object = model.poi, obs = obs997,training = data)

predict(model.rf1ROUX, obsaln, dataN10000, ntree=1000)

```
#####################  Inference des parametres 
# inference d'un parametre
Given a reg-ABC-RF object and a new value of the summary statistics, densityPlot gives the
corresponding posterior density plot of the parameter, as well as the prior (in grey)

```{r}
N1 <- rouxN10000$param$N1[modindex == "SI1"]
dataN1 <- data.frame(N1, sumstatN10000)
dataN1 <-dataN1[1:1000,]
model.rf.N1 <- regAbcrf(N1~., dataN1, ntree=500)
plot(model.rf.N1)
pdf(file="posterieurprobaTS_AM1")
densityPlot(model.rf.N1, obsaln, dataN1, ylab="density", main = "Posterior density of N1")
dev.off()
N2 <- rouxN10000$param$N2[modindex == "SI1"]
dataN2 <- data.frame(N2, sumstatN10000)
dataN2 <-dataN2[1:1000,]
model.rf.N2 <- regAbcrf(N2~., dataN2, ntree=1000)
plot(model.rf.N2)
pdf(file="posterieurprobaN2_AM1")
densityPlot(model.rf.N2, obsaln, dataN2, ylab="density", main = "Posterior density of N2")
dev.off()
####
TS <-  rouxN10000$param$TS[modindex == "AM1"]
dataTS <- data.frame(TS, sumstatN10000)
dataTS  <-dataTS[2001:3000,]
model.rf.TS <- regAbcrf(TS~., dataTS, ntree=500)
model.rf.TSC
pdf(file="posterieurprobaTS_AM")
densityPlot(model.rf.TS, obsaln, dataTS, ylab="density", main = "Posterior density of TS")
dev.off()
##
M1<-  rouxN10000$param$M12[modindex == "AM1"]
dataM1 <- data.frame(M1, sumstatN10000)
dataM1   <-dataM1[2001:3000,]
model.rf.M1<- regAbcrf(M1~., dataM1, ntree=1000)
model.rf.TM1
plot(model.rf.TM1)
pdf(file="posterieurprobaTS_AM")
densityPlot(model.rf.M1, obsaln, dataM1, ylab="density", main = "Posterior density of M1")
dev.off()
M2<-  rouxN10000$param$M21[modindex == "AM1"]
dataM2 <- data.frame(M2, sumstatN10000)
dataM2   <-dataM2[2001:3000,]
model.rf.M2<- regAbcrf(M2~., dataM2, ntree=1000)
plot(model.rf.M2)
pdf(file="posterieurprobaTS_AM")
densityPlot(model.rf.M2, obsaln, dataM2, ylab="density", main = "Posterior density of M2")
dev.off()
####TAM
TAM <-  rouxN10000$param$Tam[modindex == "AM1"]
dataTAM <- data.frame(TAM, sumstatN10000)
dataTAM  <-dataTAM[2001:3000,]
model.rf.TAM <- regAbcrf(TAM~., dataTAM, ntree=1000)
model.rf.TAM
plot(model.rf.TAM)
pdf(file="posterieurprobaTS_AM")
densityPlot(model.rf.TAM, obsaln, dataTAM, ylab="density", main = "Posterior density of TAM")
dev.off()
####REGRESSION
####classification par regression paramtre explorer TS
#The used formula means that we are interested in explaining the parameter
# TS thanks to all the remaining columns of dataTS
TS <-  rouxN10000$param$Tsplit[modindex == "AM1"]
dataTS <- data.frame(TS, sumstatN10000)
dataTS  <-dataTS[30001:40000,]
model.rf.TS <- regAbcrf(TS~., dataTS, ntree=500,min.node.size = 5, paral = TRUE, mtry =14)
model.rf.TS

#Graphical representations to access the performance of the method
errorOOB <- err.regAbcrf(object = model.rf.TS , training = dataTS,paral = TRUE)
plot(errorOOB)

# The contributions of the 25 most important summary statistics are
# represented
plot(x = model.rf.TS, n.var = 25)

###prediction
pred.obsTS <- predict(object = model.rf.TS, obs = obsaln,training = dataTS, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsTam <- predict(object = model.rf.TAM, obs = obsaln,training = dataTAM, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsM1 <- predict(object = model.rf.M1, obs = obsaln,training = dataM1, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsM2 <- predict(object = model.rf.M2, obs = obsaln,training = dataM2, quantiles = c(0.025,0.975),paral = TRUE)
# The 2.5 and 97.5 order quantiles are computed by specifying
# quantiles = c(0.025,0.975).
#Posterior mean can be retrieved by
pred.obsTS$expectation
pred.obsTS$quantiles
pred.obsTS$variance
pred.obsTam$expectation
pred.obsTam$quantiles
pred.obsTam$variance
pred.obsM1$expectation
pred.obsM1$quantiles
pred.obsM1$variance
##N1


```