---
title: "script_abc_choix_model.rmd"
author: "karine Durand"
date: "8 mars 2019"
output: html_document
---

```{r setup, include=FALSE}
#Installing and loading the R package abcrf
#install.packages("abcrf") # To install the abcrf package (version 1.6)
library(abcrf) # To load the package.
library(readr)
library("plyr", lib.loc="~/R/x86_64-pc-linux-gnu-library/3.4")
library(ggplot2)
source("formules/rbind.na.R")
source("formules/f.R")
```

## Reading data: option 2 - using a.txtfile

corresponding to the scenario indices,p columns of parameters and k columns of summary statistics, the
first row is the column labels. The field separator character being a white space.


```{r cars}
###ormule#############
paramSI1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SI_Nhomo/priorfile", col_names = T)
paramSI2 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SI_Nhetero/priorfile", col_names = T)
paramIM1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/IM_Nhomo_Mhomo/priorfile", col_names = T)
paramIM2<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/IM_Nhomo_Mhetero/priorfile", col_names = T)
paramIM3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/IM_Nhetero_Mhomo/priorfile", col_names = T)
paramIM4<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/IM_Nhetero_Mhetero/priorfile", col_names = T)
paramSC1<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SC_Nhomo_Mhomo/priorfile", col_names = T)
paramSC2<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SC_Nhomo_Mhetero/priorfile", col_names = T)
paramSC3<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SC_Nhetero_Mhomo/priorfile", col_names = T)
paramSC4<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SC_Nhetero_Mhetero/priorfile", col_names = T)
paramAM1<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/AM_Nhomo_Mhomo/priorfile", col_names = T)
paramAM2<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/AM_Nhomo_Mhetero/priorfile", col_names = T)
paramAM3<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/AM_Nhetero_Mhomo/priorfile", col_names = T)
paramAM4<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_multi_6paucast53/AM_Nhetero_Mhetero/priorfile", col_names = T)

rbind.fill(paramSI1,paramSI2,paramIM1,paramIM2,paramIM3,paramIM4,paramSC1,paramSC2,paramSC3,paramSC4,paramAM1,paramAM2,paramAM3,paramAM4)->param13paucamulti

#import des stats

SI1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SI_Nhomo/ABCstat.txt", col_names = T)
SI2 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SI_Nhetero/ABCstat.txt", col_names = T)
SC1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SC_Nhomo_Mhomo/ABCstat.txt",  col_names = T)
SC2 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SC_Nhomo_Mhetero/ABCstat.txt",  col_names = T)
SC3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SC_Nhetero_Mhomo/ABCstat.txt",  col_names = T)
SC4 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SC_Nhetero_Mhetero/ABCstat.txt",  col_names = T)

IM1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/IM_Nhomo_Mhomo/ABCstat.txt",  col_names = T)
IM2 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/IM_Nhomo_Mhetero/ABCstat.txt",  col_names = T)
IM3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/IM_Nhetero_Mhomo/ABCstat.txt",  col_names = T)
IM4 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/IM_Nhetero_Mhetero/ABCstat.txt",  col_names = T)

AM1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/AM_Nhomo_Mhomo/ABCstat.txt",  col_names = T)
AM2 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/AM_Nhomo_Mhetero/ABCstat.txt",  col_names = T)
AM3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/AM_Nhetero_Mhomo/ABCstat.txt",  col_names = T)
AM4 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/AM_Nhetero_Mhetero/ABCstat.txt",  col_names = T)
#MISSING DATA
SI1<-SI1[,2:42]
SI2<-SI2[,2:42]
SC1<-SC1[,2:42]
SC2<-SC2[,2:42]
SC3<-SC3[,2:42]
SC4<-SC4[,2:42]
IM1<-IM1[,2:42]
IM2<-IM2[,2:42]
IM3<-IM3[,2:42]
IM4<-IM4[,2:42]
AM1<-AM1[,2:42]
AM2<-AM2[,2:42]
AM3<-AM3[,2:42]
AM4<-AM4[,2:42]


SI1 <- apply(SI1 , 2, f)
SI2  <- apply(SI2  , 2, f)
SC1  <- apply(SC1  , 2, f)
SC2  <- apply(SC2  , 2, f)
SC3  <- apply(SC3  , 2, f)
SC4  <- apply(SC4  , 2, f)
IM1  <- apply(IM1  , 2, f)
IM2  <- apply(IM2  , 2, f)
IM3  <- apply(IM3  , 2, f)
IM4  <- apply(IM4  , 2, f)
AM1  <- apply(AM1  , 2, f)
AM2  <- apply(AM2  , 2, f)
AM3  <- apply(AM3  , 2, f)
AM4  <- apply(AM4  , 2, f)

rbind.na(SI1,SI2 ,IM1,IM2,IM3,IM4,SC1,SC2,SC3,SC4,AM1,AM2,AM3,AM4)->sumstat13paucamulti

obs997 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/obs/997_ortho13paucamulti_clean/997obs.txt",  col_names = T)



#param<- read_delim("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/paramtot",";", escape_double = FALSE,  trim_ws = #TRUE)
#sumsta <- read_delim("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/sumsta",  ";", escape_double = FALSE, trim_ws = TRUE)

modindex <- as.factor(c(rep("SIhomo",10000),rep("SIhetero",10000),rep("IM1",10000),rep("IM2",10000),rep("IM3",10000),rep("IM4",10000)  , rep("SC1",10000), rep("SC2",10000), rep("SC3",10000), rep("SC4",10000),rep("AM1",10000),rep("AM2",10000),rep("AM3",10000),rep("AM4",10000)))


#dfparam = as.data.frame(param)

dfparam=as.data.frame(param13paucamulti)
View(dfparam)
index1 <-as.factor(modindex) # To store the model 1 indexes.

#dfsumsta = as.data.frame(sumsta)
dfsumsta = as.data.frame(sumstat13paucamulti)
View(dfsumsta)
#n try = k/3 k nombre de summary stats =variable 42 ntry=14
paucaCVCMULTI <- list(modindex=modindex,param=dfparam, sumsta=dfsumsta)
datapaucaCVCMULTI <- data.frame(modindex, sumstat13paucamulti)
##avec une foret de 10000 arbres
model.paucaCVCMULTI<- abcrf(modindex~., data=datapaucaCVCMULTI ,ntree=600,paral = TRUE)
predict(model.paucaCVCMULTI, obs997, datapaucaCVCMULTI, ntree=500)

####VARAIANCE DES SUMMARY STATS
datapaucaCVCMULTI$corr_pi
ggplot(datapaucaCVCMULTI, aes(x=modindex, y=corr_pi)) + 
  geom_boxplot()
ggplot(datapaucaCVCMULTI, aes(x=modindex, y=bialsites_std)) + 
  geom_boxplot()


```

## PLOTS 

Confusion matrix:

```{r pressure}
model.paucaCVCMULTI
variableImpPlot(model.paucaCVCMULTI)
###courbe d'erreur en fonction du nombre d'arbre
err.rf <- err.abcrf(model.paucaCVCMULTI, datapaucaCVCMULTI)
err.rf <- err.abcrf(model.paucaCVCMULTI, datapaucaCVCMULTI_SI)
err.SI2 <- err.abcrf(model.paucaCVCMULTI, datapaucaCVCMULTI[20001:30000,])
err.IM1 <- err.abcrf(model.paucaCVCMULTI, datapaucaCVCMULTI[30001:40000,])
err.sc1 <- err.abcrf(model.paucaCVCMULTI, datapaucaCVCMULTI[60001:70000,])
err.AM1 <- err.abcrf(model.paucaCVCMULTI, datapaucaCVCMULTI[100001:120000,])
err.AM4 <- err.abcrf(model.paucaCVCMULTI, datapaucaCVCMULTI[130001:140000,])
#aec les data obs
plot(model.paucaCVCMULTI, datapaucaCVCMULTI, obs=obs997[1,])

# Prediction is complete by
pred.obsPoi <- predict(object = model.poi, obs = obs997,
training = data)
predict(model.paucaCVCMULTI, obs997, datapaucaCVCMULTI, ntree=500)
#Graphical representations to access the performance of the method
errorOOB <- err.regAbcrf(object = model.paucaCVCMULTI , training = datapaucaCVCMULTI,paral = TRUE)
plot(errorOOB)

```
#####################  Inference des parametres 
# inference d'un parametre
Given a reg-ABC-RF object and a new value of the summary statistics, densityPlot gives the
corresponding posterior density plot of the parameter, as well as the prior (in grey)

```{r}


N1 <- paucaCVCMULTI$param$N1[modindex == "AM4"]
dataN1 <- data.frame(N1, sumstat13paucamulti)
dataN1 <-dataN1[130001:140000,]
model.rf.N1 <- regAbcrf(N1~., dataN1, ntree=500)
errorOOB <- err.regAbcrf(object = model.rf.N1, training = dataN1,paral = TRUE)
res <- predictOOB(model.rf.N1, dataN1)
plot(x = model.rf.N1, n.var = 25)


plot(model.rf.N1)
pdf(file="posterieurprobaTS_AM1")
densityPlot(model.rf.N1, obs997, dataN1, ylab="density", main = "Posterior density of N1")
dev.off()
N2 <- paucaCVCMULTI$param$N2[modindex == "AM4"]
dataN2 <- data.frame(N2, sumstat13paucamulti)
dataN2 <-dataN2[130001:140000,]
model.rf.N2 <- regAbcrf(N2~., dataN2, ntree=500)
plot(model.rf.N2)
pdf(file="posterieurprobaN2_AM1")
densityPlot(model.rf.N2, obs997, dataN2, ylab="density", main = "Posterior density of N2")
dev.off()
####
TS <-  paucaCVCMULTI$param$Tsplit[modindex == "AM4"]
dataTS <- data.frame(TS, sumstat13paucamulti)
dataTS  <-dataTS[130001:140000,]
model.rf.TS <- regAbcrf(TS~., dataTS, ntree=500)
model.rf.TSC
pdf(file="posterieurprobaTS_AM")
densityPlot(model.rf.TS, obs997, dataTS, ylab="density", main = "Posterior density of TS")
dev.off()
##
M1<- paucaCVCMULTI$param$M1[modindex == "AM4"]
dataM1 <- data.frame(M1, sumstat13paucamulti)
dataM1   <-dataM1[130001:140000,]
model.rf.M1<- regAbcrf(M1~., dataM1, ntree=600)
model.rf.M1
plot(model.rf.M1)
errorOOB <- err.regAbcrf(object = model.rf.N1, training = dataN1,paral = TRUE)
pdf(file="posterieurprobaTS_AM")
densityPlot(model.rf.M1, obs997, dataM1, ylab="density", main = "Posterior density of M1")
dev.off()
M2<-  paucaCVCMULTI$param$M2[modindex == "AM4"]
dataM2 <- data.frame(M2, sumstat13paucamulti)
dataM2   <-dataM2[130001:140000,]
model.rf.M2<- regAbcrf(M2~., dataM2, ntree=500)
plot(model.rf.M2)
pdf(file="posterieurprobaTS_AM")
densityPlot(model.rf.M2, obs997, dataM2, ylab="density", main = "Posterior density of M2")
dev.off()
####TAM
TAM <-  paucaCVCMULTI$param$Tam[modindex == "AM4"]
dataTAM <- data.frame(TAM, sumstat13paucamulti)
dataTAM  <-dataTAM[130001:140000,]
model.rf.TAM <- regAbcrf(TAM~., dataTAM, ntree=500)
model.rf.TAM
plot(model.rf.TAM)
pdf(file="posterieurprobaTS_AM")
densityPlot(model.rf.TAM, obs997, dataTAM, ylab="density", main = "Posterior density of TAM")
dev.off()
####REGRESSION
####classification par regression paramtre explorer TS
#The used formula means that we are interested in explaining the parameter
# TS thanks to all the remaining columns of dataTS
TS <-  paucaCVCMULTI$param$Tsplit[modindex == "AM1"]
dataTS <- data.frame(TS, sumstat13paucamulti)
dataTS  <-dataTS[30001:40000,]
model.rf.TS <- regAbcrf(TS~., dataTS, ntree=500,min.node.size = 5, paral = TRUE, mtry =14)
model.rf.TS

#Graphical representations to access the performance of the method
errorOOB <- err.regAbcrf(object = model.rf.TS , training = dataTS,paral = TRUE)
plot(errorOOB)

# The contributions of the 25 most important summary statistics are
# represented
plot(x = model.rf.TS, n.var = 25)

###prediction
pred.obsTS <- predict(object = model.rf.TS, obs = obs997,training = dataTS, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsTam <- predict(object = model.rf.TAM, obs = obs997,training = dataTAM, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsM1 <- predict(object = model.rf.M1, obs = obs997,training = dataM1, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsM2 <- predict(object = model.rf.M2, obs = obs997,training = dataM2, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsN1 <- predict(object = model.rf.N1, obs = obs997,training = dataN1, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsN2 <- predict(object = model.rf.N2, obs = obs997,training = dataN2, quantiles = c(0.025,0.975),paral = TRUE)
# The 2.5 and 97.5 order quantiles are computed by specifying
# quantiles = c(0.025,0.975).
#Posterior mean can be retrieved by
pred.obsTS$expectation
pred.obsTS$quantiles
pred.obsTS$variance
pred.obsTam$expectation
pred.obsTam$quantiles
pred.obsTam$variance
pred.obsM1$expectation
pred.obsM1$quantiles
pred.obsM1$variance
pred.obsM2$expectation
pred.obsM2$quantiles
pred.obsM2$variance
pred.obsN1$expectation
pred.obsN1$quantiles
pred.obsN1$variance
pred.obsN2$expectation
pred.obsN2$quantiles
pred.obsN2$variance




```