---
title: "script_abc_choix_model.rmd"
author: "karine Durand"
date: "8 mars 2019"
output: html_document
---

```{r setup, include=FALSE}
#Installing and loading the R package abcrf
#install.packages("abcrf") # To install the abcrf package (version 1.6)
library(abcrf) # To load the package.
library(readr)
library("plyr", lib.loc="~/R/x86_64-pc-linux-gnu-library/3.4")
f <- function(x){
  m <- mean(x, na.rm = TRUE)
  x[is.na(x)] <- m
  x
}
```

## Reading data: option 2 - using a.txtfile

corresponding to the scenario indices,p columns of parameters and k columns of summary statistics, the
first row is the column labels. The field separator character being a white space.


```{r cars}
###ormule#############
paramSI1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/SI_Nhomo/priorfile", col_names = T)
paramSI1asym <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/SI_Nhomoasym/priorfile", col_names = T)
paramSI2 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/SI_Nhetero/priorfile", col_names = T)
paramSI2asym <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/SI_Nheteroasym//priorfile", col_names = T)
paramIM1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/IM_Nhomo_Mhomo/priorfile", col_names = T)
paramIM1asym<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/IM_Nhomoasym//priorfile", col_names = T)
paramIM3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/IM_Nhetero_Mhomo/priorfile", col_names = T)
paramIM3asym<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/IM_Nheteroasym//priorfile", col_names = T)
paramSC1<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/SC_Nhomo_Mhomo/priorfile", col_names = T)
paramSC1asym<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/SC_Nhomoasym//priorfile", col_names = T)
paramSC3<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/SC_Nhetero_Mhomo/priorfile", col_names = T)
paramSC3asym<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/SC_Nheteroasym//priorfile", col_names = T)
paramAM1<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/AM_Nhomo_Mhomo/priorfile", col_names = T)
paramAM1asym<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/AM_Nhomoasym//priorfile", col_names = T)
paramAM3<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/AM_Nhetero_Mhomo/priorfile", col_names = T)
paramAM3asym<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/AM_Nheteroasym/priorfile", col_names = T)

rbind.fill(paramSI1,paramSI1asym,paramSI2,paramSI2asym,paramIM1,paramIM1asym,paramIM3,paramIM3asym,paramSC1,paramSC1asym,paramSC3,paramSC3asym,paramAM1,paramAM1asym,paramAM3,paramAM3asym)->paramN10000
rbind.fill(paramSI1asym,paramSI2asym,paramIM1asym,paramIM3asym,paramSC1asym,paramSC3asym,paramAM1asym,paramAM3asym)->paramN10000

#import des stats

SI1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/SI_Nhomo/ABCstat.txt", col_names = T)
SI1asym <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/SI_Nhomoasym//ABCstat.txt", col_names = T)
SI3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/SI_Nhetero/ABCstat.txt", col_names = T)
SI3asym <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/SI_Nheteroasym//ABCstat.txt", col_names = T)
SC1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/SC_Nhomo_Mhomo/ABCstat.txt",  col_names = T)
SC1asym <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/SC_Nhomoasym//ABCstat.txt",  col_names = T)
SC3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/SC_Nhetero_Mhomo/ABCstat.txt",  col_names = T)
SC3asym <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/SC_Nheteroasym//ABCstat.txt",  col_names = T)

IM1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/IM_Nhomo_Mhomo/ABCstat.txt",  col_names = T)
IM1asym <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/IM_Nhomoasym//ABCstat.txt",  col_names = T)
IM3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/IM_Nhetero_Mhomo/ABCstat.txt",  col_names = T)
IM3asym <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/IM_Nheteroasym//ABCstat.txt",  col_names = T)

AM1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/AM_Nhomo_Mhomo/ABCstat.txt",  col_names = T)
AM1asym <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/AM_Nhomoasym//ABCstat.txt",  col_names = T)
AM3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/AM_Nhetero_Mhomo/ABCstat.txt",  col_names = T)
AM3asym <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_19pauca/AM_Nheteroasym//ABCstat.txt",  col_names = T)
#MISSING DATA

SI1<-SI1[,2:42]
SI1asym<-SI1asym[,2:42]
SI3<-SI3[,2:42]
SI3asym<-SI3asym[,2:42]
SC1<-SC1[,2:42]
SC1asym<-SC1asym[,2:42]
#SC2<-SC2[,2:42]
SC3<-SC3[,2:42]
SC3asym<-SC3asym[,2:42]
#SC4<-SC4[,2:42]
IM1<-IM1[,2:42]
IM1asym<-IM1asym[,2:42]
#IM2<-IM2[,2:42]
IM3<-IM3[,2:42]
IM3asym<-IM3asym[,2:42]
#IM4<-IM4[,2:42]
AM1<-AM1[,2:42]
AM1asym<-AM1asym[,2:42]
#AM2<-AM2[,2:42]
AM3<-AM3[,2:42]
AM3asym<-AM3asym[,2:42]
#AM4<-AM4[,2:42]
obs1209 <-obs1209[,2:42]
obs1209 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/obs/1209_PAUCA_nonrecomb/ABC1209obs.txt",  col_names = T)

SI1 <- apply(SI1 , 2, f)
SI1asym <- apply(SI1asym , 2, f)
SI3  <- apply(SI3  , 2, f)
SI3asym  <- apply(SI3asym  , 2, f)
SC1  <- apply(SC1  , 2, f)
SC1asym  <- apply(SC1asym  , 2, f)
#SC2  <- apply(SC2  , 2, f)
SC3  <- apply(SC3  , 2, f)
SC3asym  <- apply(SC3asym  , 2, f)
#SC4  <- apply(SC4  , 2, f)
IM1  <- apply(IM1  , 2, f)
IM1asym  <- apply(IM1asym  , 2, f)
#IM2  <- apply(IM2  , 2, f)
IM3  <- apply(IM3  , 2, f)
IM3asym  <- apply(IM3asym  , 2, f)
#IM4  <- apply(IM4  , 2, f)
AM1  <- apply(AM1  , 2, f)
AM1asym  <- apply(AM1asym  , 2, f)
#AM2  <- apply(AM2  , 2, f)
AM3  <- apply(AM3  , 2, f)
AM3asym  <- apply(AM3asym  , 2, f)
#AM4  <- apply(AM4  , 2, f)




rbind.na(SI1asym,SI3asym ,IM1asym,IM3asym,SC1asym,SC3asym,AM1asym,AM3asym)->sumstat2popspauca
rbind.na(SI1,SI1asym,SI3 ,SI3asym,IM1,IM1asym,IM3,IM3asym ,SC1,SC1asym ,SC3,SC3asym,AM1,AM1asym ,AM3,AM3asym)->sumstat2popspauca
obs1209 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/obs/1209_PAUCA_nonrecomb/ABC1209obs.txt",  col_names = T)



#param<- read_delim("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/paramtot",";", escape_double = FALSE,  trim_ws = #TRUE)
#sumsta <- read_delim("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/sumsta",  ";", escape_double = FALSE, trim_ws = TRUE)

modindex <- as.factor(c(rep("SIhomo",10000),rep("SIhetero",10000),rep("IM1",10000),rep("IM2",10000),rep("IM3",10000),rep("IM4",10000)  , rep("SC1",10000), rep("SC2",10000), rep("SC3",10000), rep("SC4",10000),rep("AM1",10000),rep("AM2",10000),rep("AM3",10000),rep("AM4",10000)))

modindex <- as.factor(c(rep("SI1asym",10000),rep("SI3asym",10000),rep("IM1asym",10000),rep("IM3asym",10000) ,rep("SC1asym",10000), rep("SC3asym",10000),rep("AM1asym",10000),rep("AM3asym",10000)))


#dfparam = as.data.frame(param)

dfparam=as.data.frame(paramN10000)
View(dfparam)
index1 <-as.factor(modindex) # To store the model 1 indexes.

#dfsumsta = as.data.frame(sumsta)
dfsumsta = as.data.frame(sumstat2popspauca)
View(dfsumsta)
#n try = k/3 k nombre de summary stats =variable 42 ntry=14
rouxN10000 <- list(modindex=modindex,param=dfparam, sumsta=dfsumsta)
dataN10000 <- data.frame(modindex, sumstat2popspauca)
model.rf1ROUX<- abcrf(modindex~., data=dataN10000 ,ntree=500,paral = TRUE)
predict(model.rf1ROUX, obs1209, dataN10000, ntree=500)

```

## PLOTS 

Confusion matrix:

```{r pressure}
model.rf1ROUX


#aec les data obs
plot(model.rf1ROUX, dataN10000, obs=obs1209[1,])
predict(model.rf1ROUX, obs1209, dataN10000, ntree=500)
err.rf <- err.abcrf(model.rf1ROUX, dataN10000)

```
#####################  Inference des parametres 
# inference d'un parametre
Given a reg-ABC-RF object and a new value of the summary statistics, densityPlot gives the
corresponding posterior density plot of the parameter, as well as the prior (in grey)

```{r}
N1 <- rouxN10000$param$N1[modindex == "AM3asym"]
dataN1 <- data.frame(N1, sumstat2popspauca)
dataN1 <-dataN1[70001:80000,]
model.rf.N1 <- regAbcrf(N1~., dataN1, ntree=500)
densityPlot(model.rf.N1, obs1209, dataN1, ylab="density", main = "Posterior density of N1")

N2 <- rouxN10000$param$N2[modindex == "AM3asym"]
dataN2 <- data.frame(N2, sumstat2popspauca)
dataN2 <-dataN2[70001:80000,]
model.rf.N2 <- regAbcrf(N2~., dataN2, ntree=500)
densityPlot(model.rf.N2, obs1209, dataN2, ylab="density", main = "Posterior density of N2")

Na <- rouxN10000$param$Na[modindex == "AM3asym"]
dataNa <- data.frame(Na,sumstat2popspauca)
dataNa <-dataNa[70001:80000,]
model.rf.Na <- regAbcrf(Na~., dataNa, ntree=500)
plot(model.rf.N2)
pdf(file="posterieurprobaN2_AM1")
densityPlot(model.rf.N2, obs1209, dataN2, ylab="density", main = "Posterior density of Na")
dev.off()
####
TS <-  rouxN10000$param$Tsplit[modindex == "AM3asym"]
dataTS <- data.frame(TS, sumstat2popspauca)
dataTS  <-dataTS[70001:80000,]
model.rf.TS <- regAbcrf(TS~., dataTS, ntree=500)
model.rf.TSC
pdf(file="posterieurprobaTS_AM")
densityPlot(model.rf.TS, obs1209, dataTS, ylab="density", main = "Posterior density of TS")
dev.off()
##
M1<-  rouxN10000$param$M1[modindex == "AM3asym"]
dataM1 <- data.frame(M1, sumstat2popspauca)
dataM1   <-dataM1[70001:80000,]
model.rf.M1<- regAbcrf(M1~., dataM1, ntree=500)
model.rf.TM1
plot(model.rf.TM1)

densityPlot(model.rf.M1, obs1209, dataM1, ylab="density", main = "Posterior density of M1")

M2<-  rouxN10000$param$M2[modindex == "AM3asym"]
dataM2 <- data.frame(M2, sumstat2popspauca)
dataM2   <-dataM2[70001:80000,]
model.rf.M2<- regAbcrf(M2~., dataM2, ntree=500)
plot(model.rf.M2)
pdf(file="posterieurprobaTS_AM")
densityPlot(model.rf.M2, obs1209, dataM2, ylab="density", main = "Posterior density of M2")
dev.off()
####TAM
TAM <-  rouxN10000$param$Tam[modindex == "AM3asym"]
dataTAM <- data.frame(TAM, sumstat2popspauca)
dataTAM  <-dataTAM[70001:80000,]
model.rf.TAM <- regAbcrf(TAM~., dataTAM, ntree=500)
model.rf.TAM
plot(model.rf.TAM)
pdf(file="posterieurprobaTS_AM")
densityPlot(model.rf.TAM, obs1209, dataTS, ylab="density", main = "Posterior density of TAM")
dev.off()
####REGRESSION
####classification par regression paramtre explorer TS
#The used formula means that we are interested in explaining the parameter
# TS thanks to all the remaining columns of dataTS
TS <-  rouxN10000$param$Tsplit[modindex == "AM1"]
dataTS <- data.frame(TS, sumstatN10000)
dataTS  <-dataTS[70001:80000,]
model.rf.TS <- regAbcrf(TS~., dataTS, ntree=500,min.node.size = 5, paral = TRUE, mtry =14)
model.rf.TS

#Graphical representations to access the performance of the method
errorOOB <- err.regAbcrf(object = model.rf.TS , training = dataTS,paral = TRUE)
plot(errorOOB)

# The contributions of the 25 most important summary statistics are
# represented
plot(x = model.rf.TS, n.var = 25)

###prediction
pred.obsTS <- predict(object = model.rf.TS, obs = obs1209,training = dataTS, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsTam <- predict(object = model.rf.TAM, obs = obs1209,training = dataTAM, quantiles = c(0.025,0.975),paral = TRUE)
  pred.obsM1 <- predict(object = model.rf.M1, obs = obs1209,training = dataM1, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsM2 <- predict(object = model.rf.M2, obs = obs1209,training = dataM1, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsN1 <- predict(object = model.rf.N1, obs = obs1209,training = dataN1, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsN2 <- predict(object = model.rf.N2, obs = obs1209,training = dataN2, quantiles = c(0.025,0.975),paral = TRUE)
pred.obsNa <- predict(object = model.rf.Na, obs = obs1209,training = dataNa, quantiles = c(0.025,0.975),paral = TRUE)
# The 2.5 and 97.5 order quantiles are computed by specifying
# quantiles = c(0.025,0.975).
#Posterior mean can be retrieved by
pred.obsTS$expectation
pred.obsTS$quantiles
pred.obsTS$variance
pred.obsTam$expectation
pred.obsTam$quantiles
pred.obsTam$variance
pred.obsM1$expectation
pred.obsM1$quantiles
pred.obsM1$variance
pred.obsM2$expectation
pred.obsM2$quantiles
pred.obsM2$variance
pred.obsN1$expectation
pred.obsN1$quantiles
pred.obsN1$variance
pred.obsN2$expectation
pred.obsN2$quantiles
pred.obsN2$variance
pred.obsNa$expectation
pred.obsNa$quantiles
pred.obsNa$variance
```