---
title: "script_abc_choix_model.rmd"
author: "karine Durand"
date: "8 mars 2019"
output: html_document
---

```{r setup, include=FALSE}
#Installing and loading the R package abcrf
#install.packages("abcrf") # To install the abcrf package (version 1.6)
library(abcrf) # To load the package.
library(readr)
library("plyr", lib.loc="~/R/x86_64-pc-linux-gnu-library/3.4")
```

## Reading data: option 2 - using a.txtfile

corresponding to the scenario indices,p columns of parameters and k columns of summary statistics, the
first row is the column labels. The field separator character being a white space.


```{r cars}
###ormule#############
paramSIhomo <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/MODIFICATIONTS30/SI_Nhomo/997", col_names = T)
paramtheta <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/MODIFICATIONTS30/AM_Nhomo_Mhomo/paramtheta", col_names = F)

#paramSIhetero <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileSINhetero", col_names = T)
paramIM1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/MODIFICATIONTS30/IM_Nhomo_Mhomo/priorfile", col_names = T)
#paramIM2<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileIMhomo_Mhetero.txt", col_names = T)
#aramIM3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileIM_Nhetero_Mhomo.txt", col_names = T)
#paramIM4<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileIMNheteroMhetero", col_names = T)
paramSC1<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/MODIFICATIONTS30/SC_Nhomo_Mhomo/priorfile", col_names = T)
#paramSC2<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileSC_Nhomo_Mhetero.txt", col_names = T)
#paramSC3<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileSC_NheteroMhomo", col_names = T)
#paramSC4<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/MODIFICATIONTS30/AM", col_names = T)
paramAM1<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/MODIFICATIONTS30/AM_Nhomo_Mhomo/temp", col_names = T)

paramAM1[997:9969999,]->paramAM1

paramtheta<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/MODIFICATIONTS30/AM_Nhomo_Mhomo/paramtheta", col_names = F)
paramtheta[997:9969999,]->paramtheta
cbind.na(paramtheta,paramAM1)->paramAM1
#paramAM2<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileAM_Nhomo_Mhetero", col_names = T)
#paramAM3<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileAMNheteroMhomo", col_names = T)
#paramAM4<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileAMNheteroMhetero", col_names = T)

rbind.fill(paramSIhomo,paramIM1,paramSC1,paramAM1)->paramRoux

#import des stats

SINhomo <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/MODIFICATIONTS30/SI_Nhomo/ABCstat.txt", col_names = T)
#SINhetero <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SI_Nhetero/ABCstat.txt", col_names = T)
SC1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/MODIFICATIONTS30/SC_Nhomo_Mhomo/ABCstat.txt",  col_names = T)
#SC2 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SC_Nhomo_Mhetero/ABCstat.txt",  col_names = T)
#SC3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SC_Nhetero_Mhomo/SC_Nhetero_Mhomo.txt",  col_names = T)
#SC4 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SC_Nhetero_Mhetero/SC_Nhetero_Mhetero.txt",  col_names = T)

IM1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/MODIFICATIONTS30/IM_Nhomo_Mhomo/ABCstat.txt",  col_names = T)
#IM2 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/IM_Nhomo_Mhetero/ABCstat.txt",  col_names = T)
#IM3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/IM_Nhetero_Mhomo/ABCstat.txt",  col_names = T)
#IM4 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/IM_Nhetero_Mhetero/IM_Nhetero_Mhetero.txt",  col_names = T)

AM1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/MODIFICATIONTS30/AM_Nhomo_Mhomo/ABC9970000",  col_names = T)
AM1[997:9969999,]->AM1 
#AM2 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/AM_Nhomo_Mhetero/ABCstat.txt",  col_names = T)
#AM3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/AM_Nhetero_Mhomo/AM_Nhetero_Mhomo.txt",  col_names = T)
#AM4 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/AM_Nhetero_Mhetero/AM_Nhetero_Mhetero.txt",  col_names = T)
#MISSING DATA
SINhomo <- apply(SINhomo , 2, f)
SINhetero  <- apply(SINhetero  , 2, f)
SC1  <- apply(SC1  , 2, f)
SC2  <- apply(SC2  , 2, f)
SC3  <- apply(SC3  , 2, f)
SC4  <- apply(SC4  , 2, f)
IM1  <- apply(IM1  , 2, f)
IM2  <- apply(IM2  , 2, f)
IM3  <- apply(IM3  , 2, f)
IM4  <- apply(IM4  , 2, f)
AM1  <- apply(AM1  , 2, f)
AM2  <- apply(AM2  , 2, f)
AM3  <- apply(AM3  , 2, f)
AM4  <- apply(AM4  , 2, f)

rbind.na(SINhomo,IM1,SC1,AM1)->sumstatRoux

obs997 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/obs/997_ortho13paucamulti_clean/997obs.txt",  col_names = T)



#param<- read_delim("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/paramtot",";", escape_double = FALSE,  trim_ws = #TRUE)
#sumsta <- read_delim("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/sumsta",  ";", escape_double = FALSE, trim_ws = TRUE)

modindex <- as.factor(c(rep("SIhomo",10000),rep("IM1",10000)  , rep("SC1",10000),rep("AM1",10000)))
modindex <- as.factor(c(rep("AM1",9969003)))


#dfparam = as.data.frame(param)
dfparam=as.data.frame(paramAM1)
dfparam=as.data.frame(paramRoux)
View(dfparam)
index1 <-as.factor(modindex) # To store the model 1 indexes.

#dfsumsta = as.data.frame(sumsta)
dfsumsta = as.data.frame(AM1)
View(dfsumsta)
#n try = k/3 k nombre de summary stats =variable 42 ntry=14
XROUX <- list(modindex=modindex,param=dfparam, sumsta=dfsumsta)
XROUX <- list(modindex=modindex,param=dfparam, sumsta=dfsumsta)
data1 <- data.frame(modindex, sumstatRoux)
model.rf1ROUX<- abcrf(modindex~., data=data1 ,ntree=3000)
model.rf1ROUX
plot(model.rf1ROUX)


#Predict and evaluate the posterior probability of the MAP for new data using an ABC-RF object
modindexA <- XROUX $modindex[1:140000]
sumstaA <- XROUX $sumsta[1:140000,]
dataA <- data.frame(modindexA, sumstaA)
model.rfA <- abcrf(modindexA~., dataA, ntree=100)
predict(model.rf1ROUX, obs997, data1, ntree=500)

#data.poi <- list(modindex=index1,param=dfparam, sumsta=dfsumsta)
```

## PLOTS 

Confusion matrix:

```{r pressure}
model.rf1


#aec les data obs
plot(model.rf1ROUX, data1, obs=obs997[1,])

# Prediction is complete by
pred.obsPoi <- predict(object = model.poi, obs = obs997,
training = data)
predict(model.rf1ROUX, obs997, data1, ntree=500)

```
#####################  Inference des parametres 
# inference d'un parametre
Given a reg-ABC-RF object and a new value of the summary statistics, densityPlot gives the
corresponding posterior density plot of the parameter, as well as the prior (in grey)

```{r}

theta <- XROUX$param$X1[modindex == "AM1"]

dataTHETA <- data.frame(theta,AM1)
dataN1 <-dataN1[30001:40000,]
model.rf.theta <- regAbcrf(theta~., dataTHETA, ntree=500)
model.rf.N1
densityPlot(model.rf.theta, obs997, dataTHETA, ylab="density", main = "Posterior density of THETA")

N1 <- XROUX $param$N1[modindex == "AM1"]
dataN1 <- data.frame(N1, sumstatRoux)
dataN1 <-dataN1[30001:40000,]
model.rf.N1 <- regAbcrf(N1~., dataN1, ntree=500)
model.rf.N1
plot(model.rf.N1)
pdf(file="posterieurprobaTS_AM1")
densityPlot(model.rf.N1, obs997, dataN1, ylab="density", main = "Posterior density of N1")
dev.off()
N2 <- XROUX $param$N2[modindex == "AM1"]
dataN2 <- data.frame(N2, sumstatRoux)
dataN2 <-dataN2[30001:40000,]
model.rf.N2 <- regAbcrf(N2~., dataN2, ntree=500)
model.rf.N2
plot(model.rf.N2)
pdf(file="posterieurprobaN2_AM1")
densityPlot(model.rf.N2, obs997, dataN2, ylab="density", main = "Posterior density of N2")
dev.off()
####
TS <-  XROUX $param$Tsplit[modindex == "AM1"]

dataTS <- data.frame(TS, sumstatRoux)
dataTS  <-dataTS[30001:40000,]
model.rf.TS <- regAbcrf(TS~., dataTS, ntree=500)
model.rf.TSC
plot(model.rf.TSC)
pdf(file="posterieurprobaTS_AM")
densityPlot(model.rf.TS, obs997, dataTS, ylab="density", main = "Posterior density of TS")
dev.off()
####REGRESSION
####classification par regression paramtre explorer TS
#The used formula means that we are interested in explaining the parameter
# TS thanks to all the remaining columns of dataTS
TS <-  XROUX $param$Tsplit[modindex == "AM1"]

dataTS <- data.frame(TS, sumstatRoux)
dataTS  <-dataTS[30001:40000,]
model.rf.TS <- regAbcrf(TS~., dataTS, ntree=500,min.node.size = 5, paral = TRUE, mtry =14)
model.rf.TS

#Graphical representations to access the performance of the method
errorOOB <- err.regAbcrf(object = model.rf.TS , training = dataTS,paral = TRUE)
plot(errorOOB)

# The contributions of the 25 most important summary statistics are
# represented
plot(x = model.rf.TS, n.var = 25)

###prediction
pred.obsTS <- predict(object = model.rf.TS, obs = obs997,training = dataTS, quantiles = c(0.025,0.975),paral = TRUE)
# The 2.5 and 97.5 order quantiles are computed by specifying
# quantiles = c(0.025,0.975).
#Posterior mean can be retrieved by
pred.obsTS$expectation
pred.obsTS$quantiles
pred.obsTS$variance
####TAM
TAM <-  XROUX $param$Tam[modindex == "AM1"]

dataTAM <- data.frame(TAM, sumstatRoux)
dataTAM  <-dataTAM[30001:40000,]
model.rf.TAM <- regAbcrf(TAM~., dataTAM, ntree=500)
model.rf.TAM
plot(model.rf.TAM)
pdf(file="posterieurprobaTS_AM")
densityPlot(model.rf.TAM, obs997, dataTS, ylab="density", main = "Posterior density of TAM")
dev.off()
##N1

N1 <- xyl$param$V2[modindex == "SI"]
sumstaN1 <- dfsumsta[1:1000,]
data3 <- data.frame(N1, sumstaN1)
model.rf.N1 <- regAbcrf(N1~., data3, ntree=500)
model.rf.N1
plot(model.rf.N1)
pdf(file="posterieurprobaN1_SI")
densityPlot(model.rf.N1, obs997, data3, ylab="density", main = "Posterior density of N1")
dev.off()
covRegAbcrf(model.rf.TS, model.rf.N1, obs997,data2, data3, ntree=500)
##NA

Na <- xyl$param$V3[modindex == "SI"]
dataNA <- data.frame(Na, sumstaN1)
model.rf.NA <- regAbcrf(N1~., data3, ntree=500)
model.rf.NA
plot(model.rf.NA)
pdf(file="posterieurprobaNA_SI")
densityPlot(model.rf.NA, obs997, dataNA, ylab="density", main = "Posterior density of NA")
dev.off()
##M12
M1<-  XROUX $param$M1[modindex == "AM1"]

dataM1 <- data.frame(M1, sumstatRoux)
dataM1   <-dataM1[100001:110000,]
model.rf.M1<- regAbcrf(M1~., dataM1, ntree=3000)
model.rf.TM1
plot(model.rf.TM1)
pdf(file="posterieurprobaTS_AM")
densityPlot(model.rf.M1, obs997, dataM1, ylab="density", main = "Posterior density of M1")
dev.off()
```