---
title: "script_abc_choix_model.rmd"
author: "karine Durand"
date: "8 mars 2019"
output: html_document
---

```{r setup, include=FALSE}
#Installing and loading the R package abcrf
#install.packages("abcrf") # To install the abcrf package (version 1.6)
library(abcrf) # To load the package.
library(readr)
library("plyr", lib.loc="~/R/x86_64-pc-linux-gnu-library/3.4")
```

## Reading data: option 2 - using a.txtfile

corresponding to the scenario indices,p columns of parameters and k columns of summary statistics, the
first row is the column labels. The field separator character being a white space.


```{r cars}
###ormule#############
paramSIhomo <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SI_Nhomo/priorfileSIhomo9999", col_names = T)
paramSIhetero <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileSINhetero", col_names = T)
paramIM1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileIMNhomoMhomo", col_names = T)
paramIM2<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileIMhomo_Mhetero.txt", col_names = T)
paramIM3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileIM_Nhetero_Mhomo.txt", col_names = T)
paramIM4<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileIMNheteroMhetero", col_names = T)
paramSC1<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileSCNhomoMhomo", col_names = T)
paramSC2<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileSC_Nhomo_Mhetero.txt", col_names = T)
paramSC3<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileSC_NheteroMhomo", col_names = T)
paramSC4<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileSCNheteroeMhetero", col_names = T)
paramAM1<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/AM_Nhomo_Mhomo/priorfile", col_names = T)
paramAM2<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileAM_Nhomo_Mhetero", col_names = T)
paramAM3<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileAMNheteroMhomo", col_names = T)
paramAM4<- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/stat_hetero/priorfileAMNheteroMhetero", col_names = T)

rbind.fill(paramSIhomo,paramSIhetero,paramIM1,paramIM2,paramIM3,paramIM4,paramSC1,paramSC2,paramSC3,paramSC4,paramAM1,paramAM2,paramAM3,paramAM4)->paramRoux

#import des stats

SINhomo <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SI_Nhomo/SI_Nomo9999", col_names = T)
SINhetero <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SI_Nhetero/ABCstat.txt", col_names = T)
SC1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SC_Nhomo_Mhomo/SC_Nhomo_Mhomo.txt",  col_names = T)
SC2 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SC_Nhomo_Mhetero/ABCstat.txt",  col_names = T)
SC3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SC_Nhetero_Mhomo/SC_Nhetero_Mhomo.txt",  col_names = T)
SC4 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/SC_Nhetero_Mhetero/SC_Nhetero_Mhetero.txt",  col_names = T)

IM1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/IM_Nhomo_Mhomo/IM_Nhomo_Mhomo.txt",  col_names = T)
IM2 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/IM_Nhomo_Mhetero/ABCstat.txt",  col_names = T)
IM3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/IM_Nhetero_Mhomo/ABCstat.txt",  col_names = T)
IM4 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/IM_Nhetero_Mhetero/IM_Nhetero_Mhetero.txt",  col_names = T)

AM1 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/AM_Nhomo_Mhomo/ABCstat.txt",  col_names = T)
AM2 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/AM_Nhomo_Mhetero/ABCstat.txt",  col_names = T)
AM3 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/AM_Nhetero_Mhomo/AM_Nhetero_Mhomo.txt",  col_names = T)
AM4 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/priorgen_13paucamulti/AM_Nhetero_Mhetero/AM_Nhetero_Mhetero.txt",  col_names = T)
#MISSING DATA
SINhomo <- apply(SINhomo , 2, f)
SINhetero  <- apply(SINhetero  , 2, f)
SC1  <- apply(SC1  , 2, f)
SC2  <- apply(SC2  , 2, f)
SC3  <- apply(SC3  , 2, f)
SC4  <- apply(SC4  , 2, f)
IM1  <- apply(IM1  , 2, f)
IM2  <- apply(IM2  , 2, f)
IM3  <- apply(IM3  , 2, f)
IM4  <- apply(IM4  , 2, f)
AM1  <- apply(AM1  , 2, f)
AM2  <- apply(AM2  , 2, f)
AM3  <- apply(AM3  , 2, f)
AM4  <- apply(AM4  , 2, f)

rbind.na(SINhomo,SINhetero,IM1,IM2,IM3,IM4,SC1,SC2,SC3,SC4,AM1,AM2,AM3,AM4)->sumstatRoux

obs997 <- read_table2("~/partage_windows/Xylella/analyses_genomiques/ABC/obs/998ortho_multi_13pauca_sansrecomb/997_obs.txt",  col_names = T)



#param<- read_delim("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/paramtot",";", escape_double = FALSE,  trim_ws = #TRUE)
#sumsta <- read_delim("~/partage_windows/Xylella/analyses_genomiques/ABC/abcrf/sumsta",  ";", escape_double = FALSE, trim_ws = TRUE)

modindex <- as.factor(c(rep("SIhomo",10000), rep("SIhetero",10000),rep("IM1",10000) , rep("IM2",10000),rep("IM3",10000),rep("IM4",10000) , rep("SC1",10000),rep("SC2",10000), rep("SC3",10000),rep("SC4",10000),rep("AM1",10000),rep("AM2",10000),rep("AM3",10000),rep("AM4",10000)))


#dfparam = as.data.frame(param)

dfparam=as.data.frame(paramRoux)
View(dfparam)
index1 <-as.factor(modindex) # To store the model 1 indexes.

#dfsumsta = as.data.frame(sumsta)
dfsumsta = as.data.frame(sumstatRoux)
View(dfsumsta)

XROUX <- list(modindex=modindex,param=dfparam, sumsta=dfsumsta)
data1 <- data.frame(modindex, sumstatRoux)
model.rf1ROUX<- abcrf(modindex~., data=data1 ,ntree=500)
model.rf1ROUX
plot(model.rf1ROUX)
#Predict and evaluate the posterior probability of the MAP for new data using an ABC-RF object
modindexA <- XROUX $modindex[1:140000]
sumstaA <- XROUX $sumsta[1:140000,]
dataA <- data.frame(modindexA, sumstaA)
model.rfA <- abcrf(modindexA~., dataA, ntree=100)
predict(model.rf1ROUX, obs997, data1, ntree=500)

#data.poi <- list(modindex=index1,param=dfparam, sumsta=dfsumsta)
```

## PLOTS 

Confusion matrix:

```{r pressure}
model.rf1


#aec les data obs
plot(model.rf1ROUX, data1, obs=obs997[1,])

# Prediction is complete by
pred.obsPoi <- predict(object = model.poi, obs = obs997,
training = data)
predict(model.rf1ROUX, obs997, data1, ntree=500)

```
#####################  Inference des parametres 
# inference d'un parametre
Given a reg-ABC-RF object and a new value of the summary statistics, densityPlot gives the
corresponding posterior density plot of the parameter, as well as the prior (in grey)

```{r}
TS <- xyl$param$V1[modindex == "SI"]

data2 <- data.frame(TS, sumstaTS)
model.rf.TS <- regAbcrf(TS~., data2, ntree=500)
model.rf.TS
plot(model.rf.TS)
pdf(file="posterieurprobaTS_SI")
densityPlot(model.rf.TS, obs997, data2, ylab="density", main = "Posterior density of TS")
dev.off()
####
TSC <- xyl$param$V7[modindex == "SC"]

dataTSC <- data.frame(TSC, sumstaTS)
model.rf.TSC <- regAbcrf(TSC~., dataTSC, ntree=500)
model.rf.TSC
plot(model.rf.TSC)
pdf(file="posterieurprobaTSC_SC")
densityPlot(model.rf.TSC, obs997, dataTSC, ylab="density", main = "Posterior density of TSC")
dev.off()
####TAM
TAM<- xyl$param$V8[modindex == "AM"]

dataTAM <- data.frame(TAM, sumstaTS)
model.rf.TAM <- regAbcrf(TAM~., dataTAM, ntree=500)
model.rf.TAM
plot(model.rf.TAM)
pdf(file="posterieurprobaTAM_AM")
densityPlot(model.rf.TSC, obs997, dataTSC, ylab="density", main = "Posterior density of TAM")
dev.off()
##N1

N1 <- xyl$param$V2[modindex == "SI"]
sumstaN1 <- dfsumsta[1:1000,]
data3 <- data.frame(N1, sumstaN1)
model.rf.N1 <- regAbcrf(N1~., data3, ntree=500)
model.rf.N1
plot(model.rf.N1)
pdf(file="posterieurprobaN1_SI")
densityPlot(model.rf.N1, obs997, data3, ylab="density", main = "Posterior density of N1")
dev.off()
covRegAbcrf(model.rf.TS, model.rf.N1, obs997,data2, data3, ntree=500)
##NA

Na <- xyl$param$V3[modindex == "SI"]
dataNA <- data.frame(Na, sumstaN1)
model.rf.NA <- regAbcrf(N1~., data3, ntree=500)
model.rf.NA
plot(model.rf.NA)
pdf(file="posterieurprobaNA_SI")
densityPlot(model.rf.NA, obs997, dataNA, ylab="density", main = "Posterior density of NA")
dev.off()
##M12

m12 <- xyl$param$V5[modindex == "IM"]
datam12 <- data.frame(m12, sumstaN1)
model.rf.m12 <- regAbcrf(m12~., datam12, ntree=500)
model.rf.m12
plot(model.rf.NA)
pdf(file="posterieurprobaM12_IM")
densityPlot(model.rf.m12, obs997, datam12, ylab="density", main = "Posterior density of M12")
dev.off()
```