---
title: "ABC classic"
author: "karine Durand"
date: "11 mars 2019"
output: html_document
---

```{r setup, include=FALSE}
library(abc)
require(abc.data)
data(musigma2)
```

## Model selection
The main model selection function is called postpr. However, before applying this function on the
real data, we perform a cross-validation for model selection (cv4postpr) to evaluate if ABC can, at
all, distinguish between the three models

```{r cars}
modindex <- c(rep("SIhomo",10000), rep("SIhetero",10000),rep("IM1",10000) , rep("IM2",10000),rep("IM3",10000),rep("IM4",10000) , rep("SC1",10000),rep("SC2",10000), rep("SC3",10000),rep("SC4",10000),rep("AM1",10000),rep("AM2",10000),rep("AM3",10000),rep("AM4",10000))
cv.modsel <- cv4postpr(modindex, sumstatRoux, nval=5, tol=.01, method="mnlogistic")
s <- summary(cv.modsel)
$tol0.01
```

Now, we may calculate the posterior probabilities of each demographic scenario using the rejection
("rejection") and the multinomial logistic regression method ("mnlogistic") of the function postpr
with a tolerance rate of 0.05%. The function summary prints out posterior model probabilities and ratios
of model probabilities (the Bayes factors) in a user-friendly way:

```{r pressure, echo=FALSE}

modsel.obs <- postpr(obs997, modindex, sumstatRoux, tol=.05, method="mnlogistic")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
